---
name: Kairi
surname: Meechoovet
position: "Esports Coordinator and Designer"
www: 
email: "kairimeechoovet@gmail.com"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
header-includes:
   - \usepackage{enumitem}
   - \setlist[itemize]{nosep, left=0pt}
   - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!requireNamespace(c("tinytex","vitae","tibble"), quietly = TRUE)) {
  install.packages(c("tinytex","vitae","tibble"))
}

if (Sys.which("pdflatex") == "" && !tinytex::is_tinytex()) {                    
  message("► TinyTeX not found – installing")
  tinytex::install_tinytex()        
} else {
  message("✓ LaTeX present – no installation needed.")
}

library(vitae)
library(tibble)
```

# Professional Summary

Passionate student at Cal Poly Pomona leading initiatives in collegiate Esports. Skilled in project and community & event management, graphic design, and copywriting with experience in organizing large-scale Esports/gaming events. Eager to learn and support marketing/event operations in the gaming industry.

# Programs

-   Figma, Google Suite, Microsoft 365

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ College, ~ Institution,
  "Bachelors of Marketing Management", "2022 – Expected Graduation 2026", "Business Administration", "California State Polytechnic University, Pomona"
) %>%
  detailed_entries(Degree, Year, College, Institution)
```

# Work Experience

```{r}
tribble(
  ~ Years, ~ Company, ~ Duties, ~ Title,

  "September 2024 – Present", "Bronco Esports",
  list(
    "Directed themes and coordinated media production for large-scale in-person Esports events–FragFest–that results in 400+ attendees. ",
    "Conceptualized and executed League of Legends-related social events such as in-houses, watch parties, and competitive tournaments, fostering community engagement in online and in-person settings. ",
    "Designed **20+** promotional graphics advertising club events that reinforced and enhanced the Bronco Esports brand identity.",
    "Assessed engagement from all Bronco Esports social media platforms to refine marketing strategies and event planning.",
    "Worked cross-functionally with Esports organizations like Gen. G and the marketing team, to develop creative promotional content from social events, generating tangible media that effectively boosted community engagement.",
    "Wrote engaging creative and informative copy for Discord announcements, Instagram, and Twitter, effectively promoting events and tournaments."
  ),
  "Marketing Lead",
  "February 2023 – Present", "Bronco Esports",
  list(
    "Led initiatives to grow the Bronco Esports League of Legends community with monthly social events/campaigns for over **150+** members.",
    "Optimized the Bronco Esports LoL Hub Discord server by restructuring roles and redesigning sections with an aesthetically pleasing design, improving navigation for new and existing users. ",
    "Consistently communicated efficiently with club members, participants, and attendees in-person and online helping events/campaigns run smoothly.",
    "Directed marketing strategies that enhanced community engagement with exclusive Discord server roles and prizes for social event/campaign participants.",
    "Frequently monitored and reported on competitor Esports club activities and Discord server operations identifying opportunities to improve engagement and event quality."
  ),
  "League of Legends Community Manager"

) %>%
  detailed_entries(
    what = Title,
    when = Years,
    with = Company,
    why = Duties
  )
```
