---
title: "Case Study: Esports Social Media Engagement Analysis"
image: "https://placehold.co/600x400?text=Case+Study"
categories: [Esports, Social Media Analytics, Twitch, Audience Growth, Content Strategy]
index: 1
---

#### **Overview**

In this project, I worked with a Tier 2 Esports organization and helped them track their engagement metrics from their digital platforms such as Twitch, Twitter, Instagram, and TikTok in order to identify what content resonates with their audience. I focused on post-tournament attraction, meme trends, and player spotlight campaigns.

::::: columns
::: {.column width="50%"}
#### **Key Insights**

-   **Memes & Highlights = 3x Engagement:** Short-form video clips of clutch replays outperformed static posts by 200%.
-   **Peak Posting Times:** 7-9 PM EST (post-tournament hours) drove the most interactions.
-   **Hashtag Strategy:** #LEAGUEOFLEGENDS and #ESPORTS boosted discoverability by 40%.
:::

::: {.column width="50%"}
#### **Key Skills Gained**

-   Social listening (Brandwatch, Sprout Social)\
-   Twitch stream overlay CTR analysis\
-   Audience Sentiment tracking (positive spikes after tournament wins)
:::
:::::

### Twitter vs Tik Tok

```{r}
# Load required package
library(ggplot2)

# Simulated engagement data
social_data <- data.frame(
  Platform = c(rep("Twitter", 5), rep("TikTok", 5)),
  Post_Type = rep(c("Meme", "Highlight", "Poll", "AMA", "Giveaway"), 2),
  Engagement_Rate = c(3.2, 4.1, 1.8, 2.5, 5.0, 8.7, 9.2, 2.1, 4.3, 12.1)
)

# Plot
ggplot(social_data, aes(x = Post_Type, y = Engagement_Rate, fill = Platform)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    title = "Esports Content Engagement by Platform",
    subtitle = "TikTok clips outperform Twitter posts by 2-3x",
    x = "Post Type",
    y = "Engagement Rate (%)"
  ) +
  theme_minimal() +
  scale_fill_manual(values = c("#1DA1F2", "#FF0050"))  # Twitter blue + TikTok red
```

### Hashtag Performance

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

# Simulated hashtag performance data across platforms
hashtag_data <- data.frame(
  Hashtag = rep(c("#LeagueOfLegends", "#Esports", "#Gaming", "#LEC"), 3),
  Platform = rep(c("TikTok", "Twitter", "Instagram"), each = 4),
  Discoverability_Lift = c(
    # TikTok performance
    52, 48, 28, 35,
    # Twitter performance
    40, 38, 15, 22,
    # Instagram performance
    45, 42, 20, 30
  )
)

# 1. Combined Platform Visualization
ggplot(hashtag_data, aes(x = reorder(Hashtag, -Discoverability_Lift), 
                       y = Discoverability_Lift, 
                       fill = Platform)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(Discoverability_Lift, "%")), 
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3) +
  scale_fill_manual(values = c("#FF0050", "#1DA1F2", "#E1306C")) + # Platform colors
  labs(
    title = "Hashtag Performance Across Platforms",
    subtitle = "#LeagueOfLegends dominates on TikTok (52% lift vs 40% on Twitter)",
    x = "",
    y = "Discoverability Lift (%)",
    fill = "Platform"
  ) +
  theme_minimal() +
  theme(legend.position = "top")

# 2. Individual Platform Visualizations (Facets)
ggplot(hashtag_data, aes(x = reorder(Hashtag, -Discoverability_Lift), 
                       y = Discoverability_Lift)) +
  geom_col(fill = "#2196F3", width = 0.7) +
  geom_text(aes(label = paste0(Discoverability_Lift, "%")), 
            vjust = -0.5, size = 3.5) +
  facet_wrap(~Platform, nrow = 1) +
  labs(
    title = "Hashtag Performance by Platform",
    subtitle = "TikTok shows highest potential for discoverability growth",
    x = "",
    y = "Discoverability Lift (%)"
  ) +
  theme_minimal() +
  theme(strip.text = element_text(face = "bold"))

# 3. Platform Comparison Heatmap
ggplot(hashtag_data, aes(x = Platform, y = Hashtag, fill = Discoverability_Lift)) +
  geom_tile(color = "white", size = 0.5) +
  geom_text(aes(label = paste0(Discoverability_Lift, "%")), color = "white", size = 4) +
  scale_fill_gradient(low = "#3F51B5", high = "#FF4081") +
  labs(
    title = "Hashtag Effectiveness Heatmap",
    x = "",
    y = "",
    fill = "Lift (%)"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))
```

### Key Insights From Data

-   Platform Differences:

    -   Tik Tok hashtags perform best overall (52% max lift)

    -   Twitter performs the worst which can suggest that our audience isn't on Twitter that much

    -   Our Instagram can improve
